Parsing Postfix Log Files

### 2009-08-27 doc/logparser-architecture.tex
Correction from Howard Hamilton: emphasise the distinction between architecture and implementation at the start of chapter 4.

To avoid cluttering the description of the parser architecture with the
details of implementing a parser for Postfix log files, each topic has been
given its own chapter.  This chapter presents the architecture developed
for this project, beginning with the overall architecture and design,
followed by detailed documentation of the three components of the
architecture: Framework, Actions, and Rules.  This chapter is focused on
the theoretical, implementation-independent aspects of the architecture;
the practical difficulties of writing a parser for Postfix log files are
covered in detail in \sectionref{Postfix Parser Implementation}.

>>>>

The parser architecture described in this chapter is flexible enough to be
used as the basis of other parsers.  Obviously it is particularly suitable
for writing parsers for log files; with judicious use of cascaded parsing
(see \sectionref{actions in architecture}), a calculator could easily be
implemented; a more ambitious project might attempt to parse a programming
language.\footnote{Lisp, where every statement is enclosed in parentheses
and can easily be isolated from the surrounding statements, might be
particularly amenable.}  To avoid cluttering the description of the
architecture with the details of implementing a parser for Postfix log
files, each topic has been given its own chapter.  This chapter is focused
on the theoretical, implementation-independent aspects of the architecture;
the practical difficulties of writing a parser for Postfix log files are
covered in detail in \sectionref{Postfix Parser Implementation}.  This
chapter presents the architecture developed for this project, beginning
with the overall architecture and design, followed by detailed
documentation of the three components of the architecture: Framework,
Actions, and Rules.
